A pipeline to analyse time-course gene expression data

### 2020-06-24 scripts/manuscript.Rmd
couple of answers

**EAP**: Why is this list not the same as the (hidden via echo=FALSE) list at
the beginning of the document? I also needed to install `BiocWorkflowTools`,
`KEGGprofile` to run the .Rmd

>>>>

**EAP**: Why is this list not the same as the (hidden via echo=FALSE) list at
the beginning of the document? I also needed to install `BiocWorkflowTools`,
`KEGGprofile` to run the .Rmd
**NV**: I think some of the libraries above are not needed anymore. Some are
also only used in hidden elements. I just checked that the whole pipeline
works, by executing all command lines the reader will see, and the libraries
are all loaded fine. I think BiocWorkflowTools is only need in the compilation
of the Rmd file.
